Old people and low-income communities are most affected by COVID-19

### 2022-02-07 outputs/paper/paper.Rmd
add readme

## Conclusion
Our findings clearly revealed that COVID-19 hits certain people and neighborhoods harder and they require more attention from the government. Luckily, the City of Toronto is aware of this situation and have launched support programs
targeting those neighborhoods. For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health conditions top priority in the vaccination program.

>>>>

# Conclusion
Our findings clearly revealed that COVID-19 hits certain people and neighborhoods harder and they require more attention from the government. Luckily, the City of Toronto is aware of this situation and have launched support programs
targeting those neighborhoods. For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health conditions top priority in the vaccination program.
